Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-15 article.tex
MHC-II

For MHC-II, we do the same analysis as MHC-I, except for
MHC-II haplotypes.

	% Transmembrane helices and strong MHC-II-binding peptides
	% were predicted for a tuberculosis reference proteome 
	% using the \verb;epitopeome; R package (\cite{epitopeome}).
	% We picked the three MHC-II alleles that are most abundant 
	% in the current human population, 
	% which are DRB4*0101, HLA-DPA10103-DPB10402 
	% \richel{
	%   We decided for DPB1*0402, but there are multiple alleles matching.
	%   I just picked the first one of the alleles matching, which are:
	%   HLA-DPA10x-DPB10402, where x equals 103-110, 201-204, 301-303 or 401
	% }
	% and DQA1*0501/DQB1*0301 \richel{reference here}
	% \frans{
	%   Neem aan dat dit die ref is naar dat stukje van most common haplotype in human population. Misschien moeten we even de coverage erbij melden. 
	%   Greenbaum, Jason, et al. "Functional classification of class II human leukocyte antigen (HLA) molecules reveals seven different supertypes and a surprising degree of repertoire sharing across supertypes." Immunogenetics 63.6 (2011): 325-335.
	% }.
	% The 5\% peptides with the lowest IC50 values were defined as binders.
	% We then simply counted the number of amino acids that were present inside the
	% cell, within the membrane or outside of the cell, as well as if it was part 
	% of a strong MHC-II binding site, as shown in figure \ref{tab:results}.

	% The \verb;epitopeome; R package (\cite{epitopeome}) binds 
	% together the \verb;tmhmm; (\cite{tmhmm}) and \verb;netmhc2pan; 
	% (\cite{netmhc2pan}) 
	% R packages. \verb;tmhmm; provides an R interface to
	% TMHMM (\cite{krogh2001predicting, sonnhammer1998hidden}), a tool
	% to predict where membrane proteins' amino acids are located within the
	% membrane.   
	% \verb;netmhc2pan; provides an R interface to
	% NetMHC2pan (\cite{jensen2018improved}), a tool
	% to predict MHC-II binding to proteins.

>>>>

\richel{Check against stupidity}
For MHC-II, we do the same analysis as MHC-I, except for
MHC-II haplotypes. We picked the top 21 MHC-II alleles that are most abundant 
in the current human population \richel{reference here}
%\frans{
%  Neem aan dat dit die ref is naar dat stukje van most common haplotype in human population. 
%  Misschien moeten we even de coverage erbij melden. 
%  Greenbaum, Jason, et al. "Functional classification of class II human leukocyte antigen (HLA) molecules reveals seven different supertypes and a surprising degree of repertoire sharing across supertypes." Immunogenetics 63.6 (2011): 325-335.
%}.
We chose to use 21 alleles to have a similar number of alleles as is done
for MHC-I.
Same as \cite{bianchi2017}, we defined the 5\% of polypeptides 
with the lowest IC50 values as binders. We then counted the percentage
of binders that have one or more amino acids that are part of a TMH.
